Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
description of linearization functions

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network. Processes in $P$ must solve the Generalized Consensus problem~\cite{Lamport05GeneralizeConsensus}. Each process receives proposals for commands of the form $\operatorname{Propose}(c)$, and it produces responses of the form $\operatorname{Decide}(\sigma)$, where $\sigma$ is a c-struct. A c-struct set is a set, containing the element $\bot$, with an append operator
$\bullet$ such that $\sigma \bullet c$ is a c-struct, for any c-struct $\sigma$ and command $c$. We say that two commands \textit{commute} when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $, for every c-struct $\sigma$. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands (see~\cite{Lamport05GeneralizeConsensus} for a complete discussion on c-struct). In the rest of the paper, unless otherwise specified, the symbol $c$, possibly sub-scripted, ranges over commands, and the symbol $\mathcal{D}$, possibly sub-scripted, ranges over sets of commands.

@@

A dependency-set algorithm exposes the input interface $\operatorname{announce}_p\left( c \right)$, to announce a command $c$, and the output interface $\operatorname{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\operatorname{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\operatorname{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\operatorname{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}

@@

A map-agreement algorithm exposes the input interface $\operatorname{propose}_p\left( c, \mathcal{D} \right)$, to propose a set of dependencies $\mathcal{D}$ for a command $c$, and the output interface $\operatorname{decide}_p\left( c, \mathcal{D} \right)$, to decide $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.
Moreover, a map-agreement algorithm must ensure that: 
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $\mathcal{D}$ is decided for a command $c$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item If $\mathcal{D}_1$ is decided for a command $c$ and $\mathcal{D}_2$ is decided for the same command $c$, then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
 \end{enumerate}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item For any decision $\operatorname{decide}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item For any two decisions $\operatorname{decide}_p\left( c, \mathcal{D}_1 \right)$, $\operatorname{decide}_q\left( c, \mathcal{D}_2 \right)$ (with $p$ possibly equal to $q$), then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.

@@

\todo{Explain the algorithm with pseudocode?}
Local variables: committed, a map from commands to dependency sets, initially the empty map.
\begin{itemize}[noitemsep,nolistsep]
    \item Upon ${propose\left( c \right)}^p$: call ${announce\left( c \right)}^p$.
    \item Upon ${suggest\left( c,d \right)}^p$: call ${propose\left( c,d \right)}^p$.
    \item Upon ${decide\left( c,d \right)}^p$: insert the mapping $c \rightarrow d$ in the map ``committed''.
    \item Periodically: process the committed commands, as described below.
\end{itemize}

The variable ``committed'' of the algorithm above can be seen as describing a directed graph $g$ whose vertices are commands and such that there is an edge from $c_1$ to $c_2$ if and only if ``committed'' maps $v_1$ to a set $deps$ where $v_2\in deps$, i.e. $v_1$ depends on $v_2$.

@@

>>>>

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network. Processes in $P$ must solve the Generalized Consensus problem~\cite{Lamport05GeneralizeConsensus}. Each process receives proposals for commands of the form $\opn{Propose}(c)$, and it produces responses of the form $\opn{Decide}(\sigma)$, where $\sigma$ is a c-struct. A c-struct set is a set, containing the element $\bot$, with an append operator
$\bullet$ such that $\sigma \bullet c$ is a c-struct, for any c-struct $\sigma$ and command $c$. We say that two commands \textit{commute} when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $, for every c-struct $\sigma$. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands (see~\cite{Lamport05GeneralizeConsensus} for a complete discussion on c-struct). In the rest of the paper, unless otherwise specified, the symbol $c$, possibly sub-scripted, ranges over commands, and the symbol $\mathcal{D}$, possibly sub-scripted, ranges over sets of commands.

@@

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, and the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}

@@

A map-agreement algorithm exposes the input interface $\opn{propose}_p\left( c, \mathcal{D} \right)$, to propose a set of dependencies $\mathcal{D}$ for a command $c$, and the output interface $\opn{decide}_p\left( c, \mathcal{D} \right)$, to decide $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.
Moreover, a map-agreement algorithm must ensure that: 
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $\mathcal{D}$ is decided for a command $c$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item If $\mathcal{D}_1$ is decided for a command $c$ and $\mathcal{D}_2$ is decided for the same command $c$, then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
 \end{enumerate}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item For any decision $\opn{decide}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item For any two decisions $\opn{decide}_p\left( c, \mathcal{D}_1 \right)$, $\opn{decide}_q\left( c, \mathcal{D}_2 \right)$ (with $p$ possibly equal to $q$), then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.

@@

\todo{Explain the algorithm with pseudocode?}

Local variables: $\opn{cs}_p$, a map from commands to dependency sets, initially the empty map.
\begin{itemize}[noitemsep,nolistsep]
    \item Upon ${\opn{propose}\left( c \right)}^p$: call ${\opn{announce}\left( c \right)}^p$.
    \item Upon ${\opn{suggest}\left( c,d \right)}^p$: call ${\opn{propose}\left( c,d \right)}^p$.
    \item Upon ${\opn{decide}\left( c,d \right)}^p$: insert the mapping $c \rightarrow d$ in the map $\opn{cs}_p$.
    \item Periodically,  every process $p$ processes $\opn{cs}_p$, as described below.
\end{itemize}

The local variable $cs_p$ of a process $p$ can be seen as describing a directed graph $g_p$ whose set of vertices $V\left( g_p \right)$ is the domain of $\opn{cs}_p$ and whose edges $E\left( g_p \right)$ are such that there is an edge from $c_1$ to $c_2$ if and only both $c_1$ and $c_2$ are in $V\left( g_p \right)$ and $v_2 \in \opn{cs}_p\left[ v_1 \right]$ (i.e., $v_1$ depends on $v_2$). For example, if $cs_p = \left[ c_1 \mapsto \aset{c_2,c_3}, c_2 \mapsto \aset{c_1} \right]$ then $V\left(
g_p \right) = \aset{c_1,c_2}$ and $E\left( g_p \right) = \aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right)}$.
Given a graph $g$, let $\opn{sccs}\left( g \right)$ be the graph whose vertices are the strongly connected components of $g$ and where there is an edge from $scc_1$ to $scc_2$ if and only if there are two vertices $v_1$ and $v_2$ of $g$ such that $v_1 \in V\left( scc_1 \right)$, $v_2 \in V\left( scc_2 \right)$, and $\left( v_1,v_2 \right)\in E\left( g \right)$. Note that $\opn{sccs}\left( g \right)$ is necessarily a forest.

Define the set of linearizations $\opn{Lins}\left( g \right)$ of a graph $g$ a the set of sequences whose length is the cardinality of $V\left( g \right)$, which contain each element of $V\left( g \right)$ exactly once, and ... \todo{or first define the partial order induced by a graph and then its compatible total orders.}

Consider a function $f$ mapping sets of commands to sequences of commands such that $f\left[ cs \right]$ contains each command in $cs$ exactly once.
A sequence of commands $cseq$ is an $f$-linearization of the graph $g$ if and only there is a sequence whose element of strongly connected

@@

\subsection{Correctenss Proof}

\subsection{Obtaining EPaxos}
